The complex network of trophic interactions in a subAntarctic Marine Protected Area

### 2023-04-06 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Add co-authors

---
title: The complex network of trophic interactions in a subAntarctic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^^,^^c^
  - name: Luciana Riccialdelli^a^
  - name: Fabiana L. Capitanio^f^
  - name: Sergio M. Delpiani^d^
  - name: Juan Martín Díaz de Astarloa^d^
  - name: Cintia Fraysse^a^
  - name: Gustavo A. Lovrich^a^
  - name: Andrea Raya Rey^a^^,^^c^^,^^e^
  - name: Mariela L. Spinelli^f^
  - name: Diego Urteaga^g^
  - name: Marcos Tatián^h^^,^^i^
  - name: Virginia A. García Alonso^f^

@@

We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research. It is worth to mention the following researchers: Daniel O. Bruno (CADIC-CONICET, Argentina), Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I. Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Laura Schejter (INIDEP-CONICET),...
Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.
This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of the MPA Namuncurá (Law 26.875).

>>>>

---
title: The complex network of trophic interactions in a subAntarctic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^^,^^c^
  - name: Luciana Riccialdelli^a^
  - name: Fabiana L. Capitanio^f^
  - name: Sergio M. Delpiani^d^
  - name: Juan Martín Díaz de Astarloa^d^
  - name: Cintia Fraysse^a^
  - name: Gustavo A. Lovrich^a^
  - name: Andrea Raya Rey^a^^,^^c^^,^^e^
  - name: Mariela L. Spinelli^f^
  - name: Diego Urteaga^g^
  - name: Marcos Tatián^h^^,^^i^
  - name: Virginia A. García Alonso^f^
  - name: Claudia C. Boy^a^
  - name: Daniel O. Bruno^a^^,^^c^

@@

We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research. It is worth to mention the following researchers: Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I. Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Laura Schejter (INIDEP-CONICET),...
Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.
This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of the MPA Namuncurá (Law 26.875).

### 2023-04-06 MS_ToSubmit/MS_Burdwood_foodweb.tex
Add co-authors

@@

      \affiliation[1]{Centro Austral de Investigaciones Cientificas
(CADIC-CONICET), Argentina}
    \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
    \affiliation[3]{Instituto de Ciencias Polares, Ambiente y Recursos
Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina}
    \affiliation[4]{Instituto de Investigaciones Marinas y Costeras
(IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina}
    \affiliation[5]{Wildlife Conservation Society, Argentina}
    \affiliation[6]{Instituto de Biodiversidad y Biología Experimental y
Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
    \affiliation[7]{Museo Argentino de Ciencias Naturales ``Bernardino
Rivadavia'', Argentina}
    \cortext[cor1]{Corresponding author}

@@

We are indebted to all those experts of the working group `Banco
Burdwood' who humbly provided their knowledge to enhance the quality of
the present research. It is worth to mention the following researchers:
Daniel O. Bruno (CADIC-CONICET, Argentina), Sandra Gordillo
(IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
Martinez (Museo Argentino de Ciencias Naturales ``Bernardino
Rivadavia'', Argentina), Laura Schejter (INIDEP-CONICET),\ldots{}
Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA
Namuncurá-Burdwood Bank and the MPA N-BB Administrators. This study was
funded by Consejo Nacional de Investigaciones Científicas y Técnicas
(CONICET) and Agencia Nacional de Promoción Científica y Tecnológica
(PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of
the MPA Namuncurá (Law 26.875).

>>>>

    \author[]{Fabiana L. Capitanio\textsuperscript{f}%
  %
  }

    \author[]{Sergio M. Delpiani\textsuperscript{d}%
  %
  }

@@

    \author[]{Marcos Tatián\textsuperscript{h,i}%
  %
  }

    \author[]{Virginia A. García Alonso\textsuperscript{f}%
  %
  }

    \author[]{Claudia C. Boy\textsuperscript{a}%
  %
  }

    \author[]{Daniel O. Bruno\textsuperscript{a,c}%
  %
  }

      \affiliation[1]{Centro Austral de Investigaciones Cientificas
(CADIC-CONICET), Argentina}
    \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
    \affiliation[3]{Instituto de Ciencias Polares, Ambiente y Recursos
Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina}
    \affiliation[4]{Instituto de Investigaciones Marinas y Costeras
(IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina}
    \affiliation[5]{Wildlife Conservation Society, Argentina}
    \affiliation[6]{Instituto de Biodiversidad y Biología Experimental y
Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
    \affiliation[7]{Museo Argentino de Ciencias Naturales ``Bernardino
Rivadavia'', Argentina}
    \affiliation[8]{Instituto de Diversidad y Ecología Animal
(IDEA-CONICET)}
    \affiliation[9]{Facultad de Ciencias Exactas, Físicas y Naturales,
Universidad Nacional de Córdoba (UNC), Argentina}
    \cortext[cor1]{Corresponding author}

@@

We are indebted to all those experts of the working group `Banco
Burdwood' who humbly provided their knowledge to enhance the quality of
the present research. It is worth to mention the following researchers:
Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba,
Argentina), Mariano I. Martinez (Museo Argentino de Ciencias Naturales
``Bernardino Rivadavia'', Argentina), Laura Schejter
(INIDEP-CONICET),\ldots{} Special thanks to G.A. Lovrich the Scientific
Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB
Administrators. This study was funded by Consejo Nacional de
Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de
Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.
This work is contribution no. XX of the MPA Namuncurá (Law 26.875).
